Supplementary Material

### 2024-10-02 manuscript/manuscript.qmd
added references.bib

Email: [jweberpals\@bwh.harvard.edu](mailto:jweberpals@bwh.harvard.edu)

@@

[**Word count:**]{.underline} 3,806 words / 4000 words

[**Tables:**]{.underline} 1

[**Figures:**]{.underline} 6

@@

[**Short running title**]{.underline}: High-dimensional multiple imputation (HDMI)

[**Keywords:**]{.underline} Missing data, Confounding, EHR, NLP, Real-World Evidence

[**Funding Statement:**]{.underline} This project was supported by Task Order 75F40119F19002 under Master Agreement 75F40119D10037 from the US Food and Drug Administration (FDA). Additional funding was provided by NIH RO1LM013204.

@@

>>>>

Email: [SWANG1\@BWH.HARVARD.EDU](SWANG1@BWH.HARVARD.EDU)

@@

[**Word count:**]{.underline} xxx words / xxx words

[**Tables:**]{.underline} x

[**Figures:**]{.underline} x

@@

[**Short running title**]{.underline}: ...

[**Keywords:**]{.underline} Real-World Evidence

[**Funding Statement:**]{.underline} This project was supported by ...

@@

... [@weberpals2024]
